The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2020-03-20 Paper/jaccardbaetica.tex
close introduction

%This paper explore--- resumir en dos líneas el objeto de estudio y definir que ha sido usado para ello dispersion of culture
This paper aims to understand the production dynamics in connection with a different areas within Roman Empire. Specifically, our work pretends to detect microeconomic processes focused on a commercial product from a specific province \citep{isaksen_network_2006}. We want to detect the pattern of olive oil production that link amphora workshops and amphoric stamps used to mark them. We focus here on exploring the economic relation between stamps and amphora production and distribution centres. To do this, an Ecology approach has been used to analyse the dispersion of stamps between amphora workshops \citep{rubio-campillo_ecology_2018}.

@@

@@

Therefore, this study proposes an evolutionary baseline to explore the distribution of Baetican olive oil production by computing spatial correlation between stamps. A way to analyse is by using a quantitative framework to measure the similarity. Here we use a ecological approach based on three steps: a) to detect similarities between stamp codes, b) to explore a potential spatial correlation and c)to establish a correlation between similarity of stamp and spatial distance.

>>>>

%This paper explore--- resumir en dos líneas el objeto de estudio y definir que ha sido usado para ello dispersion of culture
This paper aims to understand the production dynamics in connection with a different areas within Roman Empire. Specifically, our work pretends to detect microeconomic processes focused on a commercial product from a specific province \citep{isaksen_network_2006}. We want to understand the pattern of olive oil production that link amphora workshops and amphoric stamps used to mark them. We focus here on exploring the economic relation between stamps and amphora production and distribution centres. To do this, an Ecology approach has been used to analyse the dispersion of stamps between amphora workshops \citep{rubio-campillo_ecology_2018}. Stamps will be used to identify economic patterns by analysing their similarity. If workshops and provinces share stamps with similar traits then we can identify connections. By contrast, if we do not detect similar stamps then workshops worked independently.

@@

The paper is structured as follows: the next section introduces the historical context. Section two displays the dataset and the methods used for the analysis. Section three presents the results and the last section shows the discussion and the main conclusions of this work.

@@

Therefore, this study proposes an evolutionary baseline to explore the distribution of Baetican olive oil production by computing spatial correlation between stamps. A way to analyse is by using a quantitative framework to measure the similarity. Here we use a ecological approach based on three steps: a) to detect similarities between stamp codes, b)     to explore a potential spatial correlation and c) to establish a correlation between similarity of stamp and spatial distance.
